Figures

### 2019-07-08 figures/07_model-selection.Rmd
figure resize

```{r tp_summary, fig.width=3.25, fig.height=4}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[3]] # 3 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tn_summary, fig.height=4, fig.width=3.25}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

>>>>

```{r tp_summary, fig.width=4, fig.height=4.25}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[3]] # 3 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tn_summary, fig.height=4, fig.width=4.25}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
